### 2017-01-28 manuscript.rmd
Fixes text on ILS and adds citations

We next examined the possibility that ascertainment biases were differentially impacting the inference of evolution following duplication and speciation events. We focused on two possible sources of bias - node depth and branch length. We found no evidence that either affected our results (Supplementary Materials). We also examined the sensitivity of the results to the calibration times used for speciation events on the gene tree. This is important because it is expected that the most recent common ancestor of two genes that diverge due to speciation is older than the speciation event itself due to incomplete lineage sorting. There is also uncertainty associated with the timing of these speciation events. In replicate analyses we added random noise to the calibration times and found that it does not impact our inability to reject the null hypothesis (Supplementary Materials).

>>>>

We next examined the possibility that ascertainment biases were differentially impacting the inference of evolution following duplication and speciation events. We focused on two possible sources of bias - node depth and branch length. We found no evidence that either affected our results (Supplementary Materials). We also examined the sensitivity of the results to the calibration times used for speciation events on the gene trees. This is important because it is expected that genes from separate species trace backward in time to a common ancestor at older times than the splitting times of the species to which they belong [Takahata:1989uh, Degnan:2009hr]. There is also uncertainty associated with the timing of these speciation events. In replicate analyses we added random noise to the calibration times and found that it does not impact our inability to reject the null hypothesis (Supplementary Materials).
